Catchy Title Goes Here

### 2018-06-20 Paper/paper.tex
updated results text for Figure 2

\subsection{Application to DRC Data \label{subsec:DRC}}
We now turn our attention the the results of our analyses when using the real data from the DRC. As discussed in Section~\ref{subsec:BF}, we first determined which model for foi was preferred for each of the eleven provinces we used for our geographical units. We found that when all of the data was included, the only provinces that were better-described by the simple, constant-only model were Bas-Congo, Kasai Occidental, Kasai Orientale, and Maniema. When we looked at the case and vaccination data only, Equateur was also better-described by this model, and when we analyzed only the seroprevalence data, the analysis for all provinces preferred this model.

>>>>

\subsection{Application to DRC Data \label{subsec:DRC}}
%We now turn our attention the the results of our analyses when using the real data from the DRC. As discussed in Section~\ref{subsec:BF}, we first determined which model for foi was preferred for each of the eleven provinces we used for our geographical units. We found that when all of the data was included, the only provinces that were better-described by the simple, constant-only model were Bas-Congo, Kasai Occidental, Kasai Orientale, and Maniema. When we looked at the case and vaccination data only, Equateur was also better-described by this model, and when we analyzed only the seroprevalence data, the analysis for all provinces preferred this model.

For each of the 11 provinces in DRC, we fit both the constant and Weibull plus constant hazard models using age-specific case incidence and vacciation survey data, without and with the seroprevalence data from the 2014 DHS survey. When seroprevalence data were not included, the constant hazard model was selected as the best fit for Bas-Congo, Equateur, Kasai Occidental, Kasai Orientale, and Maniema.  When seroprevalence data were included in the model, the constant hazard model was selected as the best fit for Bas-Congo, Kasai Occidental, Kasai Orientale, and Maniema (FIG REF; note that panels in FIG REF 2 and FIG REF 3 are grouped into the provinces for which the Weibull plus constan, or constant hazard was selected as the best fit when all data were included in the model).  The age-specific seroprevalence estimated using only the case and vaccination coverage data tended to over-estimate the prevalence observed in the 2014 DHS and the estimate that resulted from the incluson of the serology data in the model (FIG REF). The magnitude of this bias varied from province to province; with the largest differences observed in Bandundu, Equateur, Nord Kivu, and Sud Kivu. In each of these cases, the model using only case and vaccination survey data would have given an over-estimate of the proportion immune at each age class, and thus an under-estimate of measles outbreak risk.
